Model Order Redcution of Fluid Flow While Preserving Quadratic Invariants

### 2018-07-12 sections/5.res.tex
Add error kelvin-helmholtz problem and fix labels and caption for 1D compressible Euler example.

\subsection{The Compressible Euler Equation}
\subsubsection{2D Kelvin-Helmholtz instability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Singular values KH problem %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[xlabel=$t$,
                 ylabel=$e(t)$
                 label style={font=\large},
                 legend pos=outer north east,
                 legend style={font=\large},
                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
    \end{semilogyaxis}%  
  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$. As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2\|\mathbf{p}-\mathbf{p}^r\|^2}$}.
\end{figure}

>>>>

\subsection{The Compressible Euler Equation}
\subsubsection{2D Kelvin-Helmholtz instability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[xlabel=$t$,
                 ylabel=$e(t)$,
                 label style={font=\large},
                 legend pos=outer north east,
                 legend style={font=\large},
                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
    \end{semilogyaxis}%  
  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$. As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[xlabel=$t$,
                 ylabel=$e(t)$,
                 label style={font=\large},
                 legend pos=outer north east,
                 legend style={font=\large},
                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
    \end{semilogyaxis}%  
  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$. As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2+\|\mathbf{p}-\mathbf{p}^r\|^2}$.}
\end{figure}
